A Review on Multi-Label Learning Algorithms

### 2018-01-17 Paper/Presentation/mll_review.tex
Update presentation on svm, cml

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Multi-label learning}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Introduction}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Applied to supervised classification
\begin{itemize}
\item[$\bullet$] Given input data and labels, goal is to learn a model $f: X \rightarrow Y$ 
\item[$\bullet$] $f(x_i, y_i) = r$ where $r\in \mathbb{R}$ is the confidence that $y_i$ characterizes $x_i$
\item[$\bullet$] Assume that $x_i$ belongs to $y_i$ if $r \ge $ $t(x_i)$
\begin{itemize}%[label={$\checkmark$}]
\item[$\checkmark$] $t(\cdot)$ can be a predetermined constant function or learned from $X$
\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item[$\bullet$] Transform into a label pairwise comparison ranking problem
\item[$\bullet$] For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison and use a binary algorithm $g_{jk}(x)$
\item[$\bullet$] Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. System votes for each example and if $g_{jk}(x) >0$,$x_i$ is associated with $y_j$, otherwise with $y_k$
\item[$\bullet$] For an unknown instance, all classifiers' votes are aggregated and ranked
\item[$\bullet$] A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach algorithm. One-vs-one scheme.
\item[$\bullet$] Smooths out the class-imbalance problem
\item[$\bullet$] Number of classifiers s quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item[$\circ$] Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item[$\bullet$] Decompose to an ensemble of multi-class classification problems
\item[$\bullet$] Each component targets a random subset of $\mathbb{P}(Y)$ that appears in $X$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item[$\circ$] Transform to single-label data by treating each distinct labelset as a new class
\item[$\circ$] Each example is reassigned with the new mapped class and classified through regular single-label classification
\item[$\circ$] M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
todo how does each LP classify, k-labelsets
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order approach algorithm
\item[$\bullet$] Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item[$\bullet$] Large $Y$ implies high training complexity.
\item[$\bullet$] Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item[$\bullet$] Let $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in Y_k)]$
\item[$\bullet$] Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$ to decide if to include $y_j$ in the prediction. Compute with the Bayes' theorem.
\item[$\bullet$] Priors $P(K)$ computed by smoothed frequency counting in the training data
\item[$\bullet$] Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item[$\circ$] $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item[$\circ$] $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

@@

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at feature $l$ s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Relevant-nonrelevant label pairs of $x_i$ $(y_j,y_k) \in Y_i \times \bar Y_i$ are separated by a function of their classifiers $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] Retrieves a ranked list of label pairs for each unseen instance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\end{itemize}
TODO : details of svm operation
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Labels encoded as binary random vectors into a joint pdf
\item[$\bullet$] Label correlations encoded into the joint pdf as constraints
\item[$\bullet$] Model via the maximum information entropy criterion: $H_p(x, y)$, subject to constraints $\mathbb{E_p}[f_k(x,y)] = F_k$, where $F_k$ are estimated from the training set
\item[$\bullet$] Objective arrived by Lagrange multipliers, solvable by any constraint optimization solver
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} P(y | x)$
\end{itemize}
how the fuck
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning
  % https://en.wikipedia.org/wiki/Multiple-instance_learning
\begin{itemize}
\item[$\circ$] Instead of labeled instances, get binary-labeled \emph{bags of instances}
\item[$\circ$] Assign positive label to bag if at least one member is positive
\item[$\circ$] Models complex semantics of $x_i$ in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification
  % https://en.wikipedia.org/wiki/Ordinal_regression
\begin{itemize}
\item[$\circ$] Assume labels are related through a natural ordering
\item[$\circ$] Instead of explicit class relevance, assume an ordering of
  relevance between labels via a membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

@@

%------------------------------------------------
\subsection{Online resources}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item[$\bullet$] Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item[$\bullet$] Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}

%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\Huge{\centerline{Questions?}}
\end{frame}
%------------------------------------------------
\end{document}

>>>>

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Multi-label learning}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Introduction}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Learning $\rightarrow$ build a model from data, to accomplish a task
\begin{itemize}
  \item Supervised: we have both data \emph{and labels}
\item Applied to classification in this study
\end{itemize}
Supervised classification:
\begin{itemize}
\item[$\bullet$] Given input data $X$ and labels  $Y$,
  learn the function $f: X \rightarrow Y$ 
\item[$\bullet$] $f(x_i, y_i) = r$ where $r\in \mathbb{R}$ is the confidence that $y_i$ characterizes $x_i$
\item[$\bullet$] Assume that $x_i$ belongs to $y_i$ if $r \ge $ $t(x_i)$
\begin{itemize}%[label={$\checkmark$}]
\item[$\checkmark$] $t(\cdot)$ can be a predetermined constant function or learned from $X$
\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item[$\bullet$] Transform into a label pairwise comparison ranking problem
\item[$\bullet$] For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison and use a binary algorithm $g_{jk}(x)$
\item[$\bullet$] Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$. System votes for each example and if $g_{jk}(x) >0$,$x_i$ is associated with $y_j$, otherwise with $y_k$
\item[$\bullet$] For an unknown instance, all classifiers' votes are aggregated and ranked
\item[$\bullet$] A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach algorithm. One-vs-one scheme.
\item[$\bullet$] Smooths out the class-imbalance problem
\item[$\bullet$] Number of classifiers is quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item[$\circ$] Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item[$\bullet$] Decompose to an ensemble of multi-class classification problems
\item[$\bullet$] Each component targets a random subset of $\mathbb{P}(Y)$ that appears in $X$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item[$\circ$] Transform to single-label data by treating each distinct labelset as a new class
\item[$\circ$] Each example is reassigned with the new mapped class and classified through regular single-label classification
\item[$\circ$] M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
todo how does each LP classify, k-labelsets
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] High-order approach algorithm
\item[$\bullet$] Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item[$\bullet$] Large $Y$ implies high training complexity.
\item[$\bullet$] Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item[$\bullet$] Let $H_j \equiv (y_j \in Y_i)$, $C_j = \sum_{x_k \in N(x_i)} [\delta(y_j \in Y_k)]$
\item[$\bullet$] Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$ to decide if to include $y_j$ in the prediction. Compute with the Bayes' theorem.
\item[$\bullet$] Priors $P(K)$ computed by smoothed frequency counting in the training data
\item[$\bullet$] Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item[$\circ$] $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item[$\circ$] $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

@@

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
\item[$\bullet$] Multi-label entropy is used to build a decision tree recursively
\item[$\bullet$] Split $x$ at feature $l$ s.t. the information gain criterion is maximized
\item[$\bullet$] Dataset $T$ is split on the $l$-th feature valued $\theta$ to branches ($T^-$ \& $T^+$), where $ x_{il} \leq \theta, x_i \in T^-$ and $ x_{il} > \theta, x_i \in T^+$
\item[$\bullet$] Recurse on subtrees until a stopping criterion is met (e.g. child size)
\item[$\bullet$] Single-label entropy is computed by considering labelsets as new classes
\item[$\bullet$] Assumes independence among labels to ensure low computational cost
\item[$\bullet$] Unseen instances are assigned the label of the majority of members of the leaf they arrive
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] First-order algorithm, highly efficient
\item[$\bullet$] Assumes label independence
\item[$\bullet$] Pruning and ensemble strategies proposed
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item[$\bullet$] $q$ linear classifiers $h_i(x)$, optimized with the empirical ranking loss
\item[$\bullet$] Relevant-nonrelevant label pairs of $x_i$: $(y_j,y_k) \in Y_i
  \times \bar Y_i$: decision hyperplane\footnote{w.r.t. singed classifier distance} is: $h_j, h_k$: $\left<w_j-w_k, x_i \right> + b_j - b_k=0$
\item[$\bullet$] Separation margin is the minimum distance of $x_i$ from every  $Y_i \times \bar Y_i$
\item[$\bullet$] SVM $\rightarrow$ minimize loss \emph{and} maximize margin.
  Approximate $max(\cdot)$ and introduce slack variables.

\item[$\bullet$] Ranks labels w.r.t. singled distance
\item[$\bullet$] Non-linearity achievable through feature mapping and the kernel trick
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach, maximum margin strategy
\item[$\bullet$] Convex quadratic programming problem, solved by any QP solver
\item[$\bullet$] Extensible by kernel learning: kernel selection can be overcome by Multiple Kernel Learning techniques
\item[$\bullet$] Adaptable learning by selecting an appropriate loss function
\end{itemize}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
\item[$\bullet$] Encodes labels as binary random vectors $\bm{y}=\{-1,1\}\}^q$
\item[$\bullet$] For data $x,\bm{y}$ learn joint probability distribution $p(x,\bm{y})$
\item[$\bullet$] Learn pdf $p(x,\bm{y})$ via the principle of maximun entropy
  \begin{itemize}
    \item Maximize $H_p(x,y)$ subject to $K$ constraints $\mathbb{E}[f_k(x,\bm{y})] = F_k$
    \item $f_k$ models label correlations with $F_k$ learned from the training data
  \end{itemize}
\item[$\bullet$] Optimize via Lagrange multipliers, arrive at $p(\bm{y} | x)$
\item[$\bullet$] Unseen instances labelled with $Y = \underset{y}{\text{argmax }} p(y | x)$
\end{itemize}
Pros \& cons:
\begin{itemize}
\item[$\bullet$] Second-order approach. All label pairs considered, not just relevant-irrelevant ones.
\item[$\bullet$] Convex constraint optimization problem $\rightarrow$ solvable by any
  CP solver
\item[$\bullet$] Intractable $\text{argmax}$ operation for a large label space without pruning.
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : Summary}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.45]{images/summary.png}
\caption{Summary of Representative Multi-Label Learning Algorithms}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
\item[$\bullet$] Multi-instance learning
  % https://en.wikipedia.org/wiki/Multiple-instance_learning
\begin{itemize}
\item[$\circ$] Instead of labeled instances, get binary-labeled \emph{bags of instances}
\item[$\circ$] Assign positive label to bag if at least one member is positive
\item[$\circ$] Models complex semantics of $x_i$ in input space, rather than its output
\end{itemize}
\item[$\bullet$] Ordinal classification
  % https://en.wikipedia.org/wiki/Ordinal_regression
\begin{itemize}
\item[$\circ$] Assume labels are related through a natural ordering
\item[$\circ$] Instead of explicit class relevance, assume an ordering of
  relevance between labels via a membership vector
\item[$\circ$] Transform ML problem to a set of ordinal set of problems
\end{itemize}
\item[$\bullet$] Multi-task learning
\begin{itemize}
\item[$\circ$] Multiple tasks trained in parallel, sharing information
\item[$\circ$] Knowledge from related tasks used as an inductive bias to improve generalization
\item[$\circ$] Shared or different feature space, small task workload
\end{itemize}
\item[$\bullet$] Data streams classification
\begin{itemize}
\item[$\circ$] Real-world objects are generated online and processed in  real-time
\item[$\circ$] Concept drift problem
\end{itemize}
\end{itemize}
\end{frame}

@@

%------------------------------------------------
\subsection{Online resources}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
	\begin{center}
		\includegraphics[scale = 0.47]{images/online.png}
		\caption{Online Resources for Multi-Label Learning}
	\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item[$\bullet$] Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item[$\bullet$] Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item[$\bullet$] Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Useful additional bibliography
\begin{itemize}
\item[$\bullet$] Elisseeff, André, and Jason Weston. "A kernel method for multi-labelled classification." Advances in neural information processing systems. 2002.
\item[$\bullet$]  Ghamrawi, Nadia, and Andrew McCallum. "Collective multi-label classification." Proceedings of the 14th ACM international conference on Information and knowledge management. ACM, 2005.
\end{itemize}
\end{frame}
%------------------------------------------------
\section{The end}
\begin{frame}
\Huge{\centerline{Thank you}}
\Huge{\centerline{Questions?}}
\end{frame}
%------------------------------------------------
\end{document}
